SST_patterns

### 2020-01-31 SST_patterns.Rmd
update

@@

@@

@@

OISST_filt_func <- filt_func(OISST_final)
OISST_filt_func2 <- filt_func2(OISST_final)
OISST_binding <- rbind(OISST_filt_func,OISST_filt_func2) %>% 
  select(site, product, intensity_mean)

MUR_filt_func <- filt_func(MUR_final)
MUR_filt_func2 <- filt_func2(MUR_final)
MUR_binding <- rbind(MUR_filt_func,MUR_filt_func2) %>% 
  select(site, product, intensity_mean)

G1SST_filt_func <- filt_func(G1SST_final)
G1SST_filt_func2 <- filt_func2(G1SST_final)
G1SST_binding <- rbind(G1SST_filt_func,G1SST_filt_func2) %>% 
  select(site, product, intensity_mean)

CMC_filt_func <- filt_func(CMC_final)
CMC_filt_func2 <- filt_func2(CMC_final)
CMC_binding <- rbind(CMC_filt_func,CMC_filt_func2) %>% 
  select(site, product, intensity_mean)

#write.csv(SACTN_upwell_base ,'SACTN_upwell_base .csv') # Copied this and then added in a product
rm(SACTN_upwell_base)
SACTN_mean_intensity <- SACTN_upwell_base_ %>% 
  select(site, product, intensity_mean)

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) %>% 
  select(-heading, - distance, - lat, -lon)
# write.csv(Complete_mean_intensity ,'Complete_mean_intensity .csv') # Copied this and then removedsome columnss

@@

ggplot(data = final_intensity, aes(x = product, y = intensity_mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~site)

>>>>

```{r}
knitr::opts_chunk$set(
  comment = "R>",
  warning = FALSE,
  message = FALSE 
)
#update.packages() 
library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(broom)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(data.table)
# library(plyr) # RWS: Never load the plyr package as it interferes with the tidyverse
library(heatwaveR)
library(grid)
library(ggthemes)
```

@@

# PLotting theme

```{r}
theme_Publication <- function(base_size=14, base_family="helvetica") {
      library(grid)
      library(ggthemes)
      (theme_foundation(base_size=base_size, base_family=base_family)
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.margin = unit(0, "cm"),
               #legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))

}

scale_fill_Publication <- function(...){
      library(scales)
      discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)

}

scale_colour_Publication <- function(...){
      library(scales)
      discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)

}
```

@@

CMC_dur <- read_csv("Data/CMC_dur.csv")

ggplot(data = CMC_dur, aes(x = duration)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
   labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
  scale_colour_Publication()+
  theme_Publication()

@@

OISST_filt_func <- filt_func(OISST_final)
OISST_filt_func2 <- filt_func2(OISST_final)
OISST_binding <- rbind(OISST_filt_func,OISST_filt_func2)# %>% 
 # select(site, product, intensity_mean)

MUR_filt_func <- filt_func(MUR_final)
MUR_filt_func2 <- filt_func2(MUR_final)
MUR_binding <- rbind(MUR_filt_func,MUR_filt_func2)# %>% 
 # select(site, product, intensity_mean)

G1SST_filt_func <- filt_func(G1SST_final)
G1SST_filt_func2 <- filt_func2(G1SST_final)
G1SST_binding <- rbind(G1SST_filt_func,G1SST_filt_func2) #%>% 
  #select(site, product, intensity_mean)

CMC_filt_func <- filt_func(CMC_final)
CMC_filt_func2 <- filt_func2(CMC_final)
CMC_binding <- rbind(CMC_filt_func,CMC_filt_func2) #%>% 
 # select(site, product, intensity_mean)

SACTN_filt_func <- filt_func(SACTN_upwell_base_)
SACTN_filt_func2 <- filt_func2(SACTN_upwell_base_)
SACTN_binding <- rbind(SACTN_filt_func,SACTN_filt_func2)# %>% 
# write.csv(SACTN_binding,'SACTNfinal_data.csv')

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) #%>% 
  #select(-heading, - distance, - lat, -lon)

# write.csv(Complete_mean_intensity ,'Complete_mean_intensity.csv') # Copied this and then removedsome columnss

Complete_mean_intensity2 <- Complete_mean_intensity2 %>% 
  select(-distance_km)

final_data <- rbind(Complete_mean_intensity2, SACTN_binding)
#write.csv(final_data,'final_data.csv')

@@

# PLotting

signals_average <- read_csv("Data/signals_average.csv")

ggplot(data = signals_average, aes(x = no_of_signals, y = intensity_mean)) +
  geom_point(aes(colour = product), size = 3) +
  geom_smooth(method = "lm") +
  facet_wrap(~site) + 
  labs(x = "Number of signals", y = "Average intensity") +
  scale_colour_Publication()+
  theme_Publication()
